---
author: "Leacky Muchene"
header-includes: 
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{float}
date: '`r format(Sys.time(),  "%a %d-%b-%Y %X",  tz = "CET")`'
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
    df_print: kable
    fig_caption: yes
    number_sections: true
documentclass: article
classoption: 
  - a4paper
params:
  ParametersTable: NA
  GeoDistTable: NA
  shiptype: NA
  shipname: NA
  filetimestamp: NA
title: "`r paste0('Ship Data Explorer Report: \n ')`" 
subtitle: "`r paste0('Vessel type: ',  params$shiptype, ', Vessel name: ', params$shipname)`" 
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 8,  fig.width = 8, fig.align='center', fig.pos = 'H', warning = FALSE, message = FALSE )
PkgList <- list('plyr', 'knitr',  'tidyverse', 'kableExtra') 
lapply(PkgList, function(x)do.call('require', list(x)))
```

# Introduction

The application allows a user to select a vessel (name) from a preferred vessel type. For the selection, summary note is provided indicating the ***most recent*** date for which the vessel covered the longest distance between two consecutive locations.

## Key notes
- Convert input data to feather for faster loading
- Further improvements can still be done on the app
+ Generate reports in temporary directory to keep sessions clean
+ Timestamp the report file name
+ Intensive testing before deployment to production environment
+ Add tabsets to view report within app
+ Progress bar for time consuming tasks etc
+ Implement dynamic show/hide of buttons
+ Refine report tables content and size

# Selected Vessel Parameters

A summary of the  parameters selected by the user is presented in Table \ref{tab:ParametersTable}.

```{r, ParametersTable, results='markup'}
 
knitr::kable(params$ParametersTable,  
             caption='Summary of vessel  parameters options.',
              format='latex',
             longtable=T, booktabs=T)


```



# Longest distance between consecutive locations

For the selected vessel, data corresponding to the longest distance in meters between consecutive locations is presented in Table \ref{tab:GeoDistTable}.

```{r, GeoDistTable, results='markup'}
 
knitr::kable(params$GeoDistTable,  
             caption='Summary of vessel  parameters data for longest distance covered.',
              format='latex',
             longtable=T, booktabs=T)%>% 
  kable_styling(font_size=7,   latex_options="scale_down")


```



# R Session Information
An overview of loaded packages, their versions and other relevant platform information is presented below.

```{r}
sessionInfo()
```